Autonomous Aerial for Topological Mapping of Mars Environments

### 2018-06-09 Conference/SCITECH19/SCITECH19.tex
merged evan: mostly tracking changes in .gitignore
first part of rS Sf SCITECH esults

Finally, we incorporate expected information gain and travel costs into a unified optimization. Given $d(x_c)$ from Dijkstra's cost map, the optimal candidate location is
\begin{align}
x_c^*=\argmax_{x_c}\mathcal{I}_\text{scan}(x_c,R_c^*)\mathcal B(d(x_c)),
\end{align}
and therefore the optimal pose is $X_c^*=\braces{x_c^*,R_c^*}$.

@@

The mapping, exploration, and visualization processes communicate over the Robot Operating System (ROS) framework, and Gazebo 8 serves as the simulator for the physical objects and measurements.

>>>>

Finally, we incorporate expected information gain and travel costs into a unified optimization. Given $d(x_c)$ from Dijkstra's cost map, the optimal candidate location is
\begin{align}
\label{eqn:CandidateLocationOptimization}
x_c^*=\argmax_{x_c}\mathcal{I}_\text{scan}(x_c,R_c^*)\mathcal B(d(x_c)),
\end{align}
and therefore the optimal pose is $X_c^*=\braces{x_c^*,R_c^*}$.

@@

The mapping, exploration, and visualization processes communicate over the Robot Operating System (ROS) framework, and Gazebo 8 serves as the simulator for the physical objects and measurements. There are two major programs, referred to as \emph{nodes} in ROS, used during the simulation: mapping and exploration. The mapping node takes measurements from a 3D laser scanner and pairs those with the sensor transformation relative to Mars using the ROS Transform Message Filters package. Then, it builds a 3D probabilistic map using \refeqn{RayISMAnswer}-\refeqn{Unnormalized}. The mapping node sends updates from the probabilistic map to the exploration node, which decomposes the map into $m_\text{reduced}$ according to \refeqn{Proj3DMapComb}, and builds a cost map based on Dijkstra's search to determine collision-free trajectory costs for all pose candidates. Finally, it applies \refeqn{RcStar}, \refeqn{BumpFunRecedingHorizon}, and \refeqn{CandidateLocationOptimization} to update the desired robot trajectory on a receding-horizon. An overview of the process is illustrated in Fig. \ref{fig:NodesDiagram}.

	\begin{figure}
		\centerline{
			\includegraphics[width=0.6\columnwidth]{node_diagram_3D_mars.png}
		}
		\caption{The diagram of the 3D probabilistic mapping and autonomous exploration nodes shows the primary processes and communication lines.}
		\label{fig:NodesDiagram}
	\end{figure}
